---
title: "Plotly example"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Examples of plotly

We're gonna look at NYC Airbnb data.

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

First, we did some data manipulation to get the data set ready for plotting.
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)
```

Explain:

* The `!is.na(rating)` inside of `filter()` can also be done through `drop_na(rating)` which can be added `+` outside of `filter()`.

* `%in% 100:500` means within the range from 100 to 500.



# Plotly plots

## scatterplot

Know more about `plot_ly`. Check out this [website](https://plotly-r.com/)
```{r}
?plot_ly()
```

```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)
```

Explain:
* Creating a new variable `text_label` that concatenate a couple of strings, including price and rating. 
* The `\n` in `\nRating:` means starting a new line for rating.



## boxplot

```{r}
nyc_airbnb %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

Use `fct_reorder` to order the dataset.
```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```



## bar plot

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

